Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-19 manuscript/manuscript.tex
Small edits.

For the range of epsilon parameters used, the statistical measures of repeat detection remain constant (Fig. \ref{fig:sampled_paths}).
Similarly, the runtime for each epsilon parameter remains relatively unchanged except for a slight change in the 10-genome sample.
For the 10-genome sample, the statistical measures and runtime are equivalent to when 100-500 nodes are sampled.

>>>>

The statistical measures of repeat detection remain constant across the range of epsilon parameters used in the shortest path sampling approach (Fig. \ref{fig:sampled_paths}).
Similarly, the runtime for each epsilon parameter remains relatively unchanged except for a slight change in the 10-genome sample.
The measures and runtime of the shortest path sampling approach are equivalent to when roughly 100-500 nodes are sampled in the 10-genome sample.
%For the 10-genome sample, the statistical measures and runtime are equivalent to when 100-500 nodes are sampled.
